%% 
%% TITLE PAGE FOR DOUBLE-BLIND REVIEW SUBMISSION
%% Knowledge-Based Systems Journal
%% 

\documentclass[preprint,12pt]{elsarticle}

\begin{document}

\begin{frontmatter}

\title{MedDef: An Efficient Self-Attention Model for Adversarial Resilience in Medical Imaging with Unstructured Pruning}

%% Authors with full details for title page
\author[a]{E.K. Dongbo}
\author[a]{S. Niu\corref{cor1}}
\ead{sjniu@hotmail.com}
\author[b]{P. Fero}
\author[b]{P. Bargin}
\author[c]{J.N. Kofa}

%% Author affiliations
\affiliation[a]{organization={School of Information Science and Engineering, University of Jinan},
            addressline={}, 
            city={Jinan},
            postcode={250022}, 
            state={Shandong},
            country={P.R. China}}

\affiliation[b]{organization={School of Computer Science \& Technology, Zhejiang Sci-Tech University},
            addressline={}, 
            city={Hangzhou},
            postcode={310018}, 
            state={},
            country={P.R. China}}

\affiliation[c]{organization={College of Informatics, Huazhong Agricultural University},
            addressline={}, 
            city={Wuhan},
            postcode={430070}, 
            state={},
            country={P.R. China}}

\cortext[cor1]{Corresponding author}

\end{frontmatter}

%% Declaration of interests for title page
\section*{Declaration of Interests}
The authors declare the following financial interests/personal relationships which may be considered as potential competing interests: S. Niu reports financial support was provided by National Natural Science Foundation of China. S. Niu reports financial support was provided by Natural Science Foundation of Shandong Province. S. Niu reports financial support was provided by Development Program Project of Youth Innovation Team of Institutions of Higher Learning in Shandong Province. S. Niu reports financial support was provided by Young Talent of Lifting Engineering for Science and Technology in Shandong. S. Niu reports a relationship with Key Laboratory of Intelligent Computing Technology for Network Environment, Shandong Province, School of Information Science and Engineering, University of Jinan that includes: funding grants. If there are other authors, they declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

%% Funding information
\section*{Funding}
This research was supported by the National Natural Science Foundation of China (Grant No. 62471202, 62302191), the Natural Science Foundation of Shandong Province (Grant No. ZR2023QF001), Development Program Project of Youth Innovation Team of Institutions of Higher Learning in Shandong Province (Grant No. 2023KJ315), Young Talent of Lifting Engineering for Science and Technology in Shandong (Grant No. SDAST2024QTA014), and the Key Laboratory of Intelligent Computing Technology for Network Environment, Shandong Province, School of Information Science and Engineering, University of Jinan.

\end{document}
